---
title: "Week 1 Quiz"
author: "Isaac"
date: "3/27/2022"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clear environment
rm(list = ls())
```

### Questions
4. If I execute the expression x <- 4L in R, what is the class of the object 'x' as determined by the 'class()' function?
```{r}
x <- 4L
class(x)
```

5. What is the class of the object defined by x <- c(4, TRUE)
```{r}
x <- c(4, TRUE)
class(x)
```

6. If I have two vectors x <- c(1,3,5) and y <- c(3,2,10), what is produced by the expression rbind(x, y)?
```{r}
x <-  c(1,3,5)
y <-c(3,2,10)
rbind(x,y)
```

8. Suppose I have a list defined as x <- list(2, "a", "b", TRUE). What does x[[2]] give me? Select all that apply.
```{r}
x <- list(2, "a", "b", TRUE)
x[[2]]
```

9. Suppose I have a vector x <- 1:4 and a vector y <- 2. What is produced by the expression x + y?
```{r}
x <- 1:4
y <- 2
x + y
```

10. Suppose I have a vector x <- c(3, 5, 1, 10, 12, 6) and I want to set all elements of this vector that are less than 6 to be equal to zero. What R code achieves this? Select all that apply.
```{r}
x <- c(3, 5, 1, 10, 12, 6) 
x[x >= 6] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x == 0] <- 6
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x < 6] == 0

x <- c(3, 5, 1, 10, 12, 6) 
x[x > 6] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x == 0] <- 6
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x == 6] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x <= 5] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x %in% 1:5] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x != 6] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x < 6] <- 0
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x > 0] <- 6
print(x)

x <- c(3, 5, 1, 10, 12, 6) 
x[x == 0] < 6
```

11. Use the Week 1 Quiz Data Set to answer questions 11-20.
In the dataset provided for this Quiz, what are the column names of the dataset? 
```{r}
hw1_data <- read.csv("hw1_data.csv")
colnames(hw1_data)
```

12. Extract the first 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
hw1_data[1:2,]
```

13. How many observations (i.e. rows) are in this data frame?
```{r}
nrow(hw1_data)
```

14. Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
nrow <- nrow(hw1_data)
hw1_data[(nrow-1):nrow,]
```

15. What is the value of Ozone in the 47th row?
```{r}
hw1_data$Ozone[47]
```

16. How many missing values are in the Ozone column of this data frame?
```{r}
sum(is.na(hw1_data$Ozone))
```

17. What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
mean(hw1_data$Ozone[!is.na(hw1_data$Ozone)])
```

18. Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
subset <- hw1_data[hw1_data$Ozone > 31 & hw1_data$Temp > 90, ]
subset <- subset[complete.cases(subset), ]
mean(subset$Solar.R)
```

19. What is the mean of "Temp" when "Month" is equal to 6? 
```{r}
june <- hw1_data[hw1_data$Month == 6, ]
is.na(june$Temp)
mean(june$Temp)
```

20. What was the maximum ozone value in the month of May (i.e. Month is equal to 5)
```{r}
may <- hw1_data[hw1_data$Month == 5, ]
max(may$Ozone[!is.na(may$Ozone)])
```










